---
title: "setup_notes"
author: "Dana Miller"
date: "May 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
#Install rticles
#install.packages("rticles", type = "source")
library(rticles)
```

When I try to knit `elvesier_test.Rmd`, get error:

>You are recommended to install the tinytex package to build PDF.FALSE
Error: Failed to compile elvesier_test.tex.
In addition: Warning messages:
1: In system2(..., stdout = FALSE, stderr = FALSE) :
  '"pdflatex"' not found
2: In system2(...) : '"pdflatex"' not found
Execution halted`

And opening the .tex file says "No TeX installation detetcted" 

```{r}
#install.packages("tinytex")
library(tinytex)
library(rmarkdown)
```

Next error:
>processing file: elvesier_test.Rmd
output file: elvesier_test.knit.md
Error: Failed to compile elvesier_test.tex.
In addition: Warning message:
In system2(..., stdout = FALSE, stderr = FALSE) : '"pdflatex"' not found
Execution halted

Troublshooting: 
1
```{r}
# Also does not work
render("C:/Users/Dana/3_Professional/CBE/Reproducibility/rticles_test/elvesier_test/elvesier_test.Rmd")
```

2
```{r}
# https://tex.stackexchange.com/questions/398218/pdflatex-not-found-windows
Sys.which("pdflatex")
pdflatex 
```

3 - It *will* knit as an html document, it's the pdflatex part that's not working

https://medium.com/@sorenlind/create-pdf-reports-using-r-r-markdown-latex-and-knitr-on-windows-10-952b0c48bfa9

https://rickpackblog.wordpress.com/2017/10/04/miktex-install-for-r-windows-pdf-output-r-markdown/

https://miktex.org/download

Same error after installing MikTex

```{r}
#Explicitly test that libraries for rmarkdown are included (RStudio should do this by default)
library(knitr)
library(yaml)
library(htmltools)
library(caTools)
library(bitops)
library(rmarkdown)

```

```{r}
#to edit Renviron
#install.packages("usethis")
library(usethis)

#usethis::edit_r_environ("rticles_test")
```


https://community.rstudio.com/t/how-to-set-a-variable-in-renviron/5029/3
https://stackoverflow.com/questions/33650869/how-can-i-set-the-latex-path-for-sweave-in-r 

Set . REnviron:

>#pdflatex
PATH=C:\\Users\\Dana\\AppData\\Local\\Programs\\MiKTeX 2.9\\miktex\\bin\\x64;"${PATH}"


New error:
>Output created: elvesier_test.pdf
Error in tools::file_path_as_absolute(output_file) : 
  file 'elvesier_test.pdf' does not exist
In addition: Warning message:
In readLines(logfile) : incomplete final line found on 'elvesier_test.log'


Change MikTek setting to "Install missing packages on the fly"
https://stackoverflow.com/questions/48224162/knitr-wont-compile-pdf-error-in-toolsfile-path-as-absoluteoutput-file


It worked!
